The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-07-20 manuscript.Rmd
complete using prop. to display overlap between databases and lists

```{r compare_database_overlap, fig.cap='Comparison of species by phylum across the public databases and the faunistic list. (\\#fig:database-overlap)'}
knitr::include_graphics("figures/database_overlap.pdf")
```

>>>>

```{r compare_database_overlap, fig.cap='Proportions of the total number of species by phylum that are absent from faunistic lists but are in iDigBio or OBIS ("Not in list"), and absent from iDigBio or OBIS but are in the faunistic lists ("Not in databases"). The numbers represent the number of species. (\\#fig:database-overlap)'}
knitr::include_graphics("figures/database_overlap_percent.pdf")
```
